---
title: TEPS Course Content Harvest - User Guide
format: md
---

```{r}
#| echo: false
#| output: false
library(tidyverse)
```

## Overview

This project harvests course descriptions from Norwegian teacher education institutions. It takes course codes, years, and semesters as input and produces structured data containing URLs, HTML, and extracted text from course webpages.

**Input:** A tibble as output by `rdbhapi` with course metadata (institution, course code, year, semester)

**Output:** The same tibble with added course URL, raw HTML, and extracted text

## Quick Start: Running the Pipeline

The main entry points are in `R/harvest.R`:

```{r}
#| eval: false

# Load all pipeline functions
source("R/institution_config.R")
source("R/utils.R")
source("R/add_course_url.R")
source("R/resolve_course_urls.R")
source("R/fetch_html_cols.R")
source("R/extract_fulltext.R")
source("R/checkpoint.R")
source("R/harvest_strategies.R")
source("R/harvest.R")

# Harvest a single institution
courses <- readRDS("data/courses.RDS")
result <- harvest_institution("hivolda", courses)
saveRDS(result, "data/html_hivolda.RDS")

# Or harvest all institutions at once
harvest_all()
```

### What Happens Under the Hood

1. **`get_institution_config()`**: Looks up strategy, CSS selectors, and overrides
2. **`apply_year_filter()`**: Filters to relevant years based on config
3. **`add_course_id()`**: Creates unique identifiers for each course
4. **`add_course_url()`**: Generates the correct URL for each course
5. **Strategy dispatch**: Routes to the right harvesting strategy (standard, URL discovery, etc.)
6. **`ensure_output_columns()`**: Guarantees uniform output shape

### About Checkpointing

The pipeline uses **checkpointing** to avoid re-downloading data. If the script stops or crashes:

- Already-downloaded HTML is saved in checkpoint_path, which should be updated to `data/checkpoint/html_{institution}.RDS`
- Re-running the script will skip courses already in the checkpoint
- This saves time and is polite to institutional servers

## Adding a New Institution

To add support for a new institution, you need to modify **two files**:

### 1. Add config entry to `R/institution_config.R`

```{r}
#| eval: false

# Add to the institution_configs list:
newuni = list(
  code = "1234",
  strategy = "standard",          # or url_discovery, shadow_dom, etc.
  selector = ".main-content",     # CSS selector for course plan content
  selector_mode = "single",       # "single" or "multi"
  year_in_url = TRUE
)
```

**How to find CSS selectors:**

1. Open a course page in your browser
2. Right-click on the course description text → "Inspect"
3. Look for a `class` or `id` attribute that wraps the content
4. Use the SelectorGadget tool: https://rvest.tidyverse.org/articles/selectorgadget.html
5. Test your selector to make sure it captures all course text

### 2. Add URL builder to `R/add_course_url.R`

Add a case to `case_match()` and create a URL-building function:

```{r}
#| eval: false

# In add_course_url(), add:
"newuni" ~ add_course_url_newuni(Emnekode, Årstall, Semesternavn),

# Create a helper function for your institution
add_course_url_newuni <- function(course_code, year, semester) {
  semester <- case_match(semester, "Vår" ~ "spring", "Høst" ~ "autumn")
  glue::glue("https://www.newuni.no/courses/{year}/{semester}/{tolower(course_code)}")
}
```

### 3. Test Your Changes

```{r}
#| eval: false

# Load pipeline and test
courses <- readRDS("data/courses.RDS")
result <- harvest_institution("newuni", courses, year = 2025)

# Inspect results
result |> select(Emnekode, url, html_success, extracted_text) |> head()
result$extracted_text[1]  # Inspect first result
```

Expand a little bit at a time, for example by year. Add more years as the pipeline works.

## Post-Harvest: Anonymization and Deduplication

After harvesting, run `R/run_dedup.R` to anonymize and deduplicate course plans:

```{r}
#| eval: false
source("R/run_dedup.R")
```

This runs a three-stage pipeline:

1. **Anonymize** (`anonymize_fulltext()`): Removes PII (teacher names, emails, phone numbers), dates, seasons, and administrative year references from `extracted_text`, producing a readable `course_plan` column. Content years (e.g., "etter 1945") are preserved.
2. **Normalize** (`normalize_plan_text()`): Applies lossy transforms (lowercasing, heading synonyms, blanket year removal, whitespace squishing) on `course_plan` for content hashing
3. **Deduplicate** (`deduplicate_plans()`): Groups identical normalized texts under a shared `plan_content_id`

**Output columns:**

| Column | Description |
|--------|-------------|
| `course_plan` | Anonymized, readable text (primary column for consumers) |
| `extracted_text` | Raw extracted text (kept for debugging) |
| `course_plan_normalized` | Lossy normalized text (internal, for hashing) |
| `plan_content_id` | SHA-256 hash of `course_plan_normalized` |

**Output files:**

- `data/course_offerings.RDS` — published slim dataset: course rows with DBH metadata + `plan_content_id` FK (no url, no text)
- `data/course_offerings_full.RDS` — internal working file: same rows plus `url`, `extracted_text`, `course_plan`, `course_plan_normalized`; used by the course_browser app
- `data/course_plans.RDS` — one row per unique plan per course code per institution

## Data Structure

### Input Data (`data/courses.RDS`)

The courses dataset contains:

```{r}
courses <- readRDS("data/courses.RDS")
courses |> slice(1:2)
```

Key columns:
- `institution_short`: Short code (e.g., "oslomet", "uia")
- `Emnekode_raw`: Original course code from DBH
- `Emnekode`: Normalized course code (trailing numbers removed)
- `Årstall`: Year
- `Semesternavn`: Semester name ("Vår" or "Høst")
- `Status`: Course status (1=Active, 2=New, 3=Discontinued, 4=Discontinued but exam offered)

### Output Data Structure

After processing, you'll have:

```{r}
#| echo: false
output <- tribble(
  ~course_id, ~url, ~html, ~html_success, ~extracted_text, ~course_plan,
  "oslomet_ABC123_2024_autumn_1", "https://student.oslomet.no/...", "<html>...</html>", TRUE, "ABC123 Course Description...", "ABC123 Course Description...",
  "oslomet_XYZ456_2024_spring_1", "https://student.oslomet.no/...", "<html>...</html>", TRUE, "XYZ456 Another course...", "XYZ456 Another course..."
)
output
```

- `course_plan` is the anonymized version of `extracted_text` (no names, emails, dates, or administrative years). Content years like historical references are preserved. Use this column for analysis.

## Key Functions Reference

### `add_course_id(dbh_df)`
Creates unique course identifiers combining institution, code, year, semester, and status.

### `add_course_url(df)`
Generates the correct URL for each course based on institution-specific patterns.

### `fetch_html_with_checkpoint(courses, checkpoint_path, .progress = TRUE)`
Downloads HTML from URLs with automatic checkpointing. Skips already-downloaded courses.

### `harvest_institution(institution_short, courses, year, refetch)`
Main entry point: harvests a single institution using its configured strategy.

### `harvest_all(courses, year, refetch, institutions)`
Loops through all (or specified) institutions, harvests each, saves results.

### `validate_courses(df, stage)`
Validates that required columns exist at each pipeline stage:
- `"initial"`: institution_short, Emnekode, Årstall
- `"with_url"`: institution_short, course_id, url
- `"with_html"`: institution_short, course_id, url, html, html_success

## Troubleshooting

**URLs look wrong?**
- Check your `url_pattern`
- Print a few URLs to verify: `courses |> select(url) |> head()`

**HTML download fails?**
- Check if the website is accessible
- Look at `courses$html_error` for error messages
- Some institutions may block automated requests

**Extracted text is empty or wrong?**
- Verify your CSS selector using browser dev tools
- Update selector in `R/institution_config.R` if website structure changed
- Some pages may have different structures for different years

**Checkpoint file is huge?**
- This is normal - HTML is large
- Checkpoint files are in `.gitignore` and won't be committed

## File Organization

```
├── R/
│   ├── harvest.R              # Entry points: harvest_institution(), harvest_all()
│   ├── harvest_strategies.R   # Strategy implementations
│   ├── institution_config.R   # Institution registry (strategy, selectors, overrides)
│   ├── utils.R                # Helper functions (add_course_id, validation)
│   ├── add_course_url.R       # URL generation logic
│   ├── resolve_course_urls.R  # URL discovery for USN, UiT, etc.
│   ├── fetch_html_cols.R      # HTML downloading
│   ├── extract_fulltext.R     # Config-driven text extraction
│   ├── checkpoint.R           # Checkpoint management
│   ├── anonymize.R            # PII removal: extracted_text → course_plan
│   ├── normalize_plan_text.R  # Lossy normalization for dedup hashing
│   ├── deduplicate_plans.R    # Groups identical plans by content hash
│   └── run_dedup.R            # Entry point for anonymize + dedup pipeline
├── data/
│   ├── courses.RDS            # Input course data
│   └── checkpoint/            # Checkpoint files (not in git)
└── data-raw/
    └── courses.R              # script that creates courses.RDS
```

## Need Help?

Look at the existing institution examples, but be quick to contact me, also! 🤩