---
title: TEPS Course Content Harvest - User Guide
format: md
---

```{r}
#| echo: false
#| output: false
library(tidyverse)
```

## Overview

This project harvests course descriptions from Norwegian teacher education institutions. It takes course codes, years, and semesters as input and produces structured data containing URLs, HTML, and extracted text from course webpages.

**Input:** A tibble as output by `rdbhapi` with course metadata (institution, course code, year, semester)

**Output:** The same tibble with added course URL, raw HTML, and extracted text

### Pipeline Stages

| Stage | Code | Output |
|---|---|---|
| 1. Course id `{institution}_{Emnekode_raw}_{year}_{semester}_{status}` | `add_course_id()` (`R/utils.R`) | `course_id` |
| 2. URL from metadata (institution-specific builders; NA where the URL must be discovered) | `add_course_url()` (`R/add_course_url.R`) | `url` |
| 3. URL discovery (USN, UiT, hivolda; optional) | `resolve_course_urls()` (`R/resolve_course_urls.R`) | `url`, checkpoint `data/raw/checkpoint/urls_{inst}.RDS` |
| 4. Fetch HTML with checkpointing | `fetch_html_with_checkpoint()` (`R/checkpoint.R`, `R/fetch_html_cols.R`) | `html`, `html_success`, `html_error` |
| 5. Extract text (the page's blocks as text, USN cleanup, PDF text) | `extract_fulltext_from_raw()` (`R/extract_fulltext.R`) | `data/raw/html_{inst}.RDS` (raw harvest) |
| 6. Read each stored page into blocks; the text is the blocks | `institution_blocks()`, `institution_fulltext()` (`R/pipeline.R`) | `extracted_text.RDS` |
| 7. Anonymize and deduplicate | `institution_plans()` | `course_plans.RDS`, `course_offerings*.RDS` |
| 8. Split each plan into sections | `institution_sections()` | `plan_sections.RDS` |

Stages 1-5 are run per institution by `harvest_institution()`, which dispatches
to a strategy in `R/harvest_strategies.R` (`standard`, `url_discovery`,
`shadow_dom`, `html_pdf_discovery`, `pdf_split`, `json_extract`, `noop`).
`R/institution_config.R` is the single source of truth for each institution:
strategy, the part of the page that holds the plan (`selector`, minus
`exclude`), how a plan's year is known (`plan_years`: `"url"`, `"page"` or
`"current"`), pre/post functions, fetch overrides and the
`section_*` fields. Stages 6-8 and everything after
them are a {targets} pipeline (see "Rebuilding Derived Data").

The raw harvest is append-only (#296): an institution's first harvest is
`data/raw/html_{inst}.RDS`, every later one adds
`data/raw/harvests/{date}/html_{inst}.RDS` with what it fetched, and no raw
file is written twice (see "Raw Store and Finalized Releases"). The
steps after it rebuild everything from it with the current code, so a changed
selector or post function needs `targets::tar_make()`, not a new harvest. A
page is read once into blocks (see "Blocks and Sections"), and both the
`extracted_text` and the sections are made from them. The `extracted_text` saved with the harvest is not used
downstream, except for plans that came from a PDF (uis archive plans,
steiner): the PDF is not kept, so that text is the raw data.

## Quick Start: Running the Pipeline

The main entry points are in `R/harvest.R`:

```{r}
#| eval: false

# Load all pipeline functions
source("R/utils.R")
source("R/add_course_url.R")
source("R/resolve_course_urls.R")
source("R/fetch_html_cols.R")
source("R/extract_fulltext.R")
source("R/section_heading_map.R")
source("R/blocks.R")
source("R/institution_config.R")
source("R/checkpoint.R")
source("R/harvest_strategies.R")
source("R/harvest.R")

# Harvest a single institution
courses <- readRDS("data/input/courses.RDS")
result <- harvest_institution("hivolda", courses)
saveRDS(result, "data/raw/html_hivolda.RDS")

# Only one year, or ignore the checkpoints and fetch again
result <- harvest_institution("oslomet", courses, year = 2025)
result <- harvest_institution("ntnu", courses, refetch = TRUE)

# Or harvest all institutions at once (saves data/raw/html_{inst}.RDS)
harvest_all()
```

The source order matters: `R/institution_config.R` refers to functions defined
in `R/fetch_html_cols.R` and `R/extract_fulltext.R`.

### What Happens Under the Hood

1. **`get_institution_config()`**: Looks up strategy, CSS selectors, and overrides
2. **`apply_year_filter()`**: Filters to relevant years based on config
3. **`add_course_id()`**: Creates unique identifiers for each course
4. **`add_course_url()`**: Generates the correct URL for each course
5. **Strategy dispatch**: Routes to the right harvesting strategy (standard, URL discovery, etc.)
6. **`ensure_output_columns()`**: Guarantees uniform output shape

### About Checkpointing

The pipeline uses **checkpointing** to avoid re-downloading data. If the script stops or crashes:

- Already-downloaded HTML is saved in `data/raw/checkpoint/html_{institution}.RDS` (`course_id`, `html`, `html_success`, `html_error`)
- Re-running the script fetches only courses not in the checkpoint (anti-join by `course_id`)
- This saves time and is polite to institutional servers

The checkpoint only resumes an interrupted harvest; it is a cache, not the
record. Offerings already in a raw file are skipped by `harvest_all()` itself
(see "Raw Store and Finalized Releases"). For "page" and "current" sites
(`plan_years`) the checkpoint is removed before every harvest, because their
pages change over time and an old copy must not stand in for a new one.

### Rebuilding Derived Data

Everything after the harvest is a {targets} pipeline: `_targets.R` lists the
steps, `R/pipeline.R` holds their functions. Run it after a harvest or after
changing code or config:

```{r}
#| eval: false
targets::tar_make()               # rebuild whatever is outdated
targets::tar_outdated()           # what would be rebuilt, without building
targets::tar_read(metrics_check)  # changes against the metrics snapshot
targets::tar_read(unmapped)       # headings the section extractor could not map
targets::tar_read(heading_use)    # pages per heading-map pattern (0 = unused)
targets::tar_read(privacy_check)  # personal data found in data/processed/
targets::tar_read(frozen_check)   # changes to the finalized release (empty before one)
targets::tar_read(gaps)           # course-years without a plan, and why
```

{targets} keeps each step's result in `_targets/` (gitignored) together with a
hash of its inputs and of the code it calls, and reruns a step only when one of
those changed. The steps per institution (fulltext, plans, sections, unmapped
headings, fetch status) run once per institution: a new raw file of uib, or a change to
uib's entry in `R/institution_config.R`, rebuilds only uib, while a change to
shared code (`R/anonymize.R`, `R/section_heading_map.R`,
`R/extract_sections.R`) reruns that step for every institution. The pipeline
writes the data files in `data/interim/` and `data/processed/` (see "Data Files: Published and Internal"),
`app/course_browser/data/browser_data.RDS`, the OJS Parquet files, `data/data_notes.md`
and `methods.md`. The harvest is not part of it.

`methods.md` (from `methods.qmd`) holds the choices behind the data that an
article's methods section must report, by topic, with numbers computed from the
data; a decision that changes what the data mean gets an entry there.
`data/interim/plan_gaps.RDS` (target `gaps`) lists every course-year without a
plan with the reason (no URL, 404, fetch error, page but no plan) and flags
the gaps between two years with plans, the ones worth checking by hand; the
data notes summarize it ("Course-years without a plan").

The steps run on 4 local worker processes ({crew}, set in `tar_option_set()`
in `_targets.R`), several institutions at a time. A full build takes about 11
minutes (2026-10-06). To debug a step with `browser()`, run in the current session instead:
`targets::tar_make(callr_function = NULL, use_crew = FALSE)`.

The pipeline ends by comparing the built data with a snapshot of
per-institution and per-section counts and median text lengths
(`R/pipeline_metrics.R`, `tests/snapshots/pipeline_metrics.csv`). Changes
beyond tolerance show as a warning in `tar_make()` and make
`tests/testthat/test-pipeline-metrics.R` fail. When a change is intended,
update the snapshot and commit it together with the change:

```{r}
#| eval: false
source("R/pipeline_metrics.R")
check_pipeline_metrics(update = TRUE)
```

Per-institution prose notes are edited directly in `data/data_notes.qmd`.

### Packages and Tests

Package versions are pinned with renv: `renv.lock` records R 4.6.1 and every
package the code uses, and R started in this folder loads them from the
project library in `renv/` (activated by `.Rprofile`). On a new machine,
`renv::restore()` installs them. After adding a package, record it with
`renv::snapshot()` and commit `renv.lock`.

The tests run with `testthat::test_dir("tests/testthat")`, and on GitHub
Actions for every push and pull request to main
(`.github/workflows/tests.yml`, packages from `renv.lock`). Tests that need
the harvested or built data (only `data/input/` is in git), a browser or external URLs
skip themselves there.

## Adding a New Institution

To add support for a new institution, you need to modify **two files**. In
Claude Code, the `/add-institution` skill walks through the same steps.

### 1. Add config entry to `R/institution_config.R`

```{r}
#| eval: false

# Add to the institution_configs list:
newuni = list(
  code = "1234",                  # DBH code; several if it changed: c("0264", "1177")
  strategy = "standard",          # or url_discovery, shadow_dom, etc.
  selector = ".main-content",     # the element that holds the course plan
  exclude = ".contact",           # optional: parts of it that are not the plan
  plan_years = "url",             # year in the URL; "page" or "current": see R/institution_config.R
  section_strategy = "html"       # how the plan is split; see "Blocks and Sections"
)
```

**How to find CSS selectors:**

1. Open a course page in your browser
2. Right-click on the course description text → "Inspect"
3. Look for a `class` or `id` attribute that wraps the content
4. Use the SelectorGadget tool: https://rvest.tidyverse.org/articles/selectorgadget.html
5. Test your selector to make sure it captures all course text

`selector` names one element (the first match is used); choose the
narrowest element that holds the whole plan, and leave out navigation,
contact boxes (staff names) and widgets inside it with `exclude` (uis, mf,
hivolda do this).

### 2. Add URL builder to `R/add_course_url.R`

Add a case to `case_match()` and create a URL-building function:

```{r}
#| eval: false

# In add_course_url(), add:
"newuni" ~ add_course_url_newuni(Emnekode, Årstall, Semesternavn),

# Create a helper function for your institution
add_course_url_newuni <- function(course_code, year, semester) {
  semester <- case_match(semester, "Vår" ~ "spring", "Høst" ~ "autumn")
  glue::glue("https://www.newuni.no/courses/{year}/{semester}/{tolower(course_code)}")
}
```

### 3. Test Your Changes

```{r}
#| eval: false

# Load pipeline and test
courses <- readRDS("data/input/courses.RDS")
result <- harvest_institution("newuni", courses, year = 2025)

# Inspect results
result |> select(Emnekode, url, html_success, extracted_text) |> head()
result$extracted_text[1]  # Inspect first result
```

Expand a little bit at a time, for example by year. Add more years as the pipeline works.

For standard institutions no changes to `R/extract_fulltext.R` or
`R/harvest_strategies.R` are needed. Sites that need a browser (Shadow DOM),
PDF splitting or URL discovery need a strategy function in
`R/harvest_strategies.R`.

## Post-Harvest: Anonymization and Deduplication

The pipeline anonymizes and deduplicates the course plans in three stages:

1. **Anonymize** (`anonymize_text()`): Removes PII (teacher names, emails, phone numbers, staff lists "Name (Role)", signature lines "Name, dekan"), dates, seasons, and administrative year references ("Opprettet 2020", "2023/2024") from `extracted_text`, producing a readable `course_plan` column. Content years (e.g., "etter 1945", "NOU 2015:2") are preserved. Institution-specific handlers (`.anon_*()`) run first, then the generic cleanup (`.anon_generic()`).
2. **Normalize** (`normalize_plan_text()`): Applies lossy transforms (lowercasing, heading synonyms, blanket year removal, whitespace squishing) on `course_plan` for content hashing
3. **Deduplicate** (`deduplicate_plans()`): Groups identical normalized texts under a shared `plan_content_id`

**Output columns:**

| Column | Description |
|--------|-------------|
| `course_plan` | Anonymized, readable text (primary column for consumers) |
| `extracted_text` | Raw extracted text (kept for debugging) |
| `course_plan_normalized` | Lossy normalized text (internal, for hashing) |
| `plan_content_id` | SHA-256 hash of `course_plan_normalized` |
| `plan_year_basis` | How the plan's year is known: `url`, `page` or `current` (`plan_years` in the config) |
| `harvested_at` | For `current` sites: the date of the harvest the page comes from |

A page with no section to read and under 1,500 characters is a page shell,
not a plan (`SHELL_MAX_NCHAR`, #222): its offerings keep their text but get no
`plan_content_id`.

### Sites that show only the current plan

UiO, MF, NMBU and Steiner (`plan_years = "current"`) publish only the plan in
force, without a year in the URL. A harvest therefore holds the plans of the
academic year (August-July) it was made in, and a later harvest cannot recover
them. Their raw files are snapshots (#293):

- Each harvest of such a site fetches the pages of its latest DBH year again
  and adds them as a dated raw file, stamped `harvested_at`. Checkpoints from
  an earlier academic year are removed first (they would return last year's
  pages), and a harvest in June-August warns (the site may already show next
  year's plan).
- `read_harvest()` gives each offering the page of its course code from the
  latest harvest in the offering's academic year (autumn Y: Y/Y+1, spring Y:
  Y-1/Y), or no page. A page counts for its course and year whichever DBH row
  it was fetched for, so DBH rows published years later still find it.
- So harvest these sites once in every academic year (best September-November
  or February-April), whether or not DBH has a new year; a year without a
  harvest has no plans for them.

Their harvests are all dated: `data/raw/harvests/2026-04-04/` (the user's
earlier harvest, 2025/26) and `2026-09-30/` (2026/27). A harvest date comes
from the `harvested_at` column or the directory name, never from the file's
modification time, which a copy changes. The rest of the April backup, for
sites with the year in the URL, is in `data/backup/2026-04-04/` and is not read.
Raw files exist only locally: back them up.

A "page" site (NLA) and a "current" site change their pages over time, so
their checkpoints are removed before every harvest and all pages are fetched
again; for "url" sites the checkpoint only resumes an interrupted harvest.

### Raw Store and Finalized Releases

No raw file is written twice (#296). `harvest_all()` saves an institution's
first harvest to `data/raw/html_{inst}.RDS`; a later harvest fetches only the
offerings no raw file holds yet (a current site: a new snapshot) and saves them
to `data/raw/harvests/{date}/html_{inst}.RDS`. `harvest_all(year = 2026)` and
`harvest_all()` therefore both just add what is new. `read_harvest()` combines
the files; an offering in two files stops the build.

To finalize a release, after `tar_make()` and tagging the commit:

```r
source("R/utils.R"); source("R/release.R")
finalize_release("data-YYYY-MM-DD")   # then commit tests/snapshots/raw_manifest.csv
release_data("data-YYYY-MM-DD")       # hand-over to the coding project
```

`finalize_release()` makes every raw file read-only (an overwrite then fails),
lists them with md5 sums in `tests/snapshots/raw_manifest.csv`, and keeps the
release's offerings, plans and sections in `data/releases/{tag}/`. On every
build `tar_read(frozen_check)` lists any change to the release: a raw file
changed or missing, an offering gone or linked to another plan, a plan gone or
with other text, a section changed. Plans
added later (a new DBH year) are not changes. A planned change to the release
(a privacy fix) means a new release: finalize it, and `release_data()` writes
the old -> new `plan_content_id` crosswalk.

**Output files:**

- `data/processed/course_offerings.RDS` — published slim dataset: course rows with DBH metadata + `plan_content_id` FK (no url, no text)
- `data/interim/course_offerings_full.RDS` — internal working file: same rows plus `url`, `extracted_text`, `course_plan`, `course_plan_normalized`; used by the course_browser app
- `data/processed/course_plans.RDS` — one row per unique plan per course code per institution, with the offering its text comes from (`source_course_id`)

## Post-Harvest: Section Extraction

The pipeline splits each course plan into its parts and writes
`data/processed/plan_sections.RDS` with one row per plan and section
(`plan_content_id`, `institution`, `Emnekode`, `source_course_id`, `section`,
`text`), keyed like `course_plans.RDS`. A plan's sections are cut from the page
of `source_course_id`, the offering whose text the plan keeps, so they match
its `course_plan`. The seven sections are
`course_content`, `learning_outcomes`, `teaching_methods`, `assessment`,
`coursework_requirements`, `prerequisites` and `reading_list`. Section text is
anonymized with the same `anonymize_text()` as `course_plan`: sections are cut
from the raw `html`/`extracted_text`, so this step must keep anonymizing.
Admission text, exam logistics and placeholder rows such as "Se fagplanen." are
left out.

`tar_read(metrics)` has the number of plans with each section per
institution and `pct_text_in_sections`, the median share of a plan's text
that its sections hold (what is left is metadata, admission text, exam
logistics and headings the map does not know). `tar_read(unmapped)` lists the
headings the extractor could not map, with the number of pages each is on,
and `tar_read(heading_use)` every pattern of the heading map with the pages
it opens a section on: a pattern on no page is a candidate for removal (the
html reader's text fallback, used for uis PDF plans, is not counted). To map a new heading, add a pattern to
`R/section_heading_map.R`; how each institution is split is set by the
`section_*` fields in `R/institution_config.R`.

### Blocks and Sections

Each page is read once into a **block table** (`R/blocks.R`): one row per
heading, sub-heading or piece of text, in document order, with the section a
heading maps to. `sectionize()` (`R/extract_sections.R`) then walks the blocks
with the same rules for every institution: a heading opens its section (an
unmapped one closes it), a sub-heading switches section only inside a mapped
one, and text goes to the open section. What differs between institutions is
how their pages are read, set by `section_strategy` and the other `section_*`
fields in `R/institution_config.R`:

| `section_strategy` | Institutions | Reads |
|---|---|---|
| `html` | oslomet, uia, ntnu, inn, hiof, hivolda, hvl, mf, nord, nih, uib, uio, uis, uit, nmbu | The DOM under `selector`. Falls back to `text` when it finds < 3 sections |
| `json` | nla | Titles and contents in the embedded EmneplanPage JSON |
| `text` | usn, steiner (+ the fallback, e.g. uis PDF plans) | Heading-shaped lines in `extracted_text`; skips a table of contents ("Innholdsfortegnelse", usn); inside a reading list opened by a whole heading only a whole heading switches section (book titles) |
| `noop` | samas | — |

Fields for the `html` reader:

- `selector` and `exclude` (shared with the fulltext): the container, and
  elements in it that are not read (mf's facts box, contact card and banner;
  nord's "Kopier lenke" label).
- `section_heading_selector`: section headings (default `h2`; ntnu
  `"h2, h3"` for its "Eksamen" block, inn's `div.label`, uib's and mf's
  `summary`, nord's `button.ac-trigger`).
- `section_scope`: elements that hold a section of their own (`details`,
  nord's `div.ac`); the section open around them continues after them.
- `section_initial`: section for text before the first heading (mf's untitled
  intro is course_content).
- `section_untitled`: elements that hold a section without a heading, as
  `c(selector = section)` (nord's short description `div.placeholder-text`
  is course_content; the title and course code before it stay out).
- `section_fields`: hivolda's Drupal fields (`div.field-<name>`) are the
  headings, each mapped to a section by its class name; text outside the
  fields (title, programmes) is in the fulltext but in no section.
- `section_subheading_selector`: elements inside a section that switch to
  another section (uio `"h3, h4, p"`; `"p"` for uia, oslomet, hiof, hvl, nmbu;
  mf's intro paragraphs). A `<p>` counts if its whole text (minus a trailing
  colon) equals a heading pattern, or if its leading `<em>`/`<strong>` run or
  its first or last `<br>`-separated line does (uia `<p><em>Faget i
  praksis</em>I løpet …</p>`). A whole-bold `<p>` that names no section is a
  group label: it ends a sub-section and returns to the parent. Sub-headings
  act only under a mapped heading (oslomet's programme "Fagplan" block stays
  out); one naming the section already open ("Kunnskap") stays as content. A
  `<p>` in a list item is skipped unless that `<li>` holds a section heading
  (oslomet's accordion). An unmapped `h3` ("Karakterskala") hands its text
  back to the parent section, keeping the heading as its first line. A
  colon-ended lead-in naming a coursework gate ("… følgende obligatoriske
  aktiviteter:") starts coursework_requirements.

Other fields:

- `section_text_header`: regex for a title + metadata block at the top of
  `extracted_text` (uis PDFs: "Emnekode:", "Tilbys av:"); the `text` reader
  skips it and files the untitled paragraph after it as course_content.
- `section_inline_coursework`: move "Arbeidskrav (AK): …" / "Obligatorisk
  deltakelse …" lines from assessment to coursework_requirements (nord).
- `section_pointer`: a section whose text is only a pointer to another block
  of the page ("Se fagplanen.") takes the text under a sub-heading of that
  block, after a lead naming the source. oslomet: teaching methods from the
  subject's "Fagplan" block ("Fagets arbeids- og undervisningsformer"), as
  "Se fagplanen. Fagplanen sier: …" (#289).

### Heading Map and Cleanup

`match_heading_to_section()` (`R/section_heading_map.R`) checks exact equality
against every pattern first, then substring patterns in table order (first hit
wins; rows with `exact = TRUE` only match whole headings). The `text` reader
passes `word_start = TRUE` so "elevkunnskap" does not match "kunnskap", and only
accepts heading-shaped lines (capitalised, ≤ 8 words, no digits, no "Label:
value", no closing full stop). Patterns mapped to `".drop"` end the current
section and their text is discarded: admission headings ("Opptak til emnet",
"Opptakskrav", "Hvem kan ta dette emnet?") and exam logistics ("Mer om eksamen
ved UiO", "Hjelpemidler", "Sensorordning", resit headings such as "Ny/utsatt
eksamen"). Exam language and grading scale stay in assessment.

HTML is parsed by `.read_doc()`, which drops `script`, `style`, `select` and
`label` (ntnu script text, uib semester picker); the `json` reader parses the
page itself because its data is in a `<script>`.

A prerequisites label inside course_content ("Forkunnskapskrav", uit's "Om
emnet") moves the paragraph it names to prerequisites
(`.split_inline_prerequisites()`), and a paragraph of 40 or more characters
that its section repeats is kept once.

`.clean_sections()` removes `.drop` rows, strips notices and page widgets from
assessment/coursework (`.section_noise`: plagiarism and ChatGPT/COVID notices,
uib banner and footer, flattened exam-table headers, …), removes admission
sentences from prerequisites (`.strip_admission_lines()`), drops
placeholder-only rows (`.placeholder_phrases`: "Ingen", "Se fagplanen.", "-",
Leganto pointers, "Oppgis senere.", "… ikke publisert ennå"), and drops a first
line that only repeats the section heading (but keeps learning-outcome group
labels such as "Kunnskap").

## Auditing a Pipeline Step

The `/audit-institutions <sections|fulltext|anonymization> [inst ...]` skill
(Claude Code) checks a pipeline step for every institution with one review
agent per institution. R scripts build a review packet per institution
(`R/audit/prepare_{check}.R`; for sections after the deterministic pre-pass
`R/audit/qa_sections.R`), the agents write findings to
`data/audit/{check}/findings/{inst}.json`, and `R/audit/aggregate.R` verifies
them (course ids and verbatim quotes must be in the packet) and writes a ranked
cross-institution report. Details: `.claude/skills/audit-institutions/SKILL.md`.

## Data Files: Published and Internal

Files that hold raw page text (`html`, `extracted_text`) contain staff names,
e-mail addresses and phone numbers and are never published. Everything that is
shared is built from the anonymized text (`anonymize_text()`). The data are
kept in one folder per stage, so the folder says what may be shared:

| Folder | Holds | Written by | In git |
|---|---|---|---|
| `data/input/` | the DBH course list, the pipeline input | `data-raw/courses.R` | yes |
| `data/raw/` | the harvest, with personal data; append-only | harvesting only | no |
| `data/releases/{tag}/` | offerings, plans and sections of a finalized release | `finalize_release()` | no |
| `data/backup/` | earlier harvests kept but not read (personal data) | by hand | no |
| `data/interim/` | text rebuilt from the harvest, with personal data; never shared | `targets::tar_make()` | no |
| `data/processed/` | anonymized data or data without text; can be shared | `targets::tar_make()` | no |

`data/processed/` may only hold text that went through `anonymize_text()`. The
pipeline checks this on every build: target `privacy_check` scans the files for
e-mail addresses, phone numbers, "Name (Role)" lines and "Name, dekan"
signatures and warns, and `tests/testthat/test-anonymize.R` fails, on any hit.
The repository is public.

| File | Contents | Personal data | Status |
|---|---|---|---|
| `data/input/courses.RDS` | DBH course metadata (pipeline input) | none | in git |
| `data/raw/html_{inst}.RDS`, `data/raw/harvests/{date}/`, `data/raw/checkpoint/` | raw harvest: `html` (+ `extracted_text` from harvest time) | yes (raw) | internal |
| `data/interim/plan_gaps.RDS` | course-years without a plan, reason, URLs tried | none | internal |
| `data/interim/extracted_text.RDS` | `extracted_text` rebuilt from the raw harvest | yes (raw) | internal |
| `data/interim/course_offerings_full.RDS` | offerings + `url`, `extracted_text`, `course_plan` | yes (`extracted_text`) | internal |
| `data/processed/course_offerings.RDS` | DBH metadata + `plan_content_id`, no text | none | published |
| `data/processed/course_plans.RDS` | anonymized `course_plan` (+ `course_plan_normalized`) | anonymized | published |
| `data/processed/plan_sections.RDS` | anonymized section `text` per plan | anonymized | publishable |
| `app/course_browser/data/browser_data.RDS` | course_browser payload: plans, offering metadata, sections | anonymized (no `extracted_text`) | internal (app) |
| `app/course_browser_ojs/data/*.parquet` | anonymized `course_plan` + slim offering metadata | anonymized | published with the OJS page (build artifact) |
| `data/audit/` | audit findings (quotes from anonymized text) | staff names redacted | in git |

The scan catches text that skipped the anonymizer, not names the anonymizer
misses; the anonymization audit (`/audit-institutions anonymization`) checks
that per institution.

## Data Structure

### Input Data (`data/input/courses.RDS`)

The courses dataset contains:

```{r}
courses <- readRDS("data/input/courses.RDS")
courses |> slice(1:2)
```

Key columns:
- `institution`: Short code (e.g., "oslomet", "uia")
- `Emnekode_raw`: Original course code from DBH (used in `course_id`)
- `Emnekode`: Course code with the trailing version number removed (`canon_remove_trailing_num()`: "ABC123-1" → "ABC123")
- `Årstall`: Year
- `Semesternavn`: Semester name ("Vår" or "Høst"; `canon_semester_name()` maps Vår/Høst/Sommer to spring/autumn/summer)
- `Status`: Course status (1=Active, 2=New, 3=Discontinued, 4=Discontinued but exam offered)

DBH lists most courses under both semesters of a year, also when they are
taught in one. Where pages are semester-specific, about half the rows therefore
have no plan by design; see "Semester registration in DBH" in
`data/data_notes.qmd` before reading row-level success rates.

### Output Data Structure

After processing, you'll have:

```{r}
#| echo: false
output <- tribble(
  ~course_id, ~url, ~html, ~html_success, ~extracted_text, ~course_plan,
  "oslomet_ABC123_2024_autumn_1", "https://student.oslomet.no/...", "<html>...</html>", TRUE, "ABC123 Course Description...", "ABC123 Course Description...",
  "oslomet_XYZ456_2024_spring_1", "https://student.oslomet.no/...", "<html>...</html>", TRUE, "XYZ456 Another course...", "XYZ456 Another course..."
)
output
```

- `course_plan` is the anonymized version of `extracted_text` (no names, emails, dates, or administrative years). Content years like historical references are preserved. Use this column for analysis.

## Institution-Specific Notes

**NORD.** The URL needs Norwegian characters in the semester parameter
(`HØST`/`VÅR`); ASCII `HOEST` falls back to a generic "Gjeldende
emnebeskrivelse" page without year-specific content. The site maps each
semester to its academic year (`VÅR&year=2023` gives the 2022/23 plan). Pattern:
`https://www.nord.no/studier/emner/{code}?year={year}&semester={HØST|VÅR}`.

**NTNU.** The URL has the year but not the semester. A page saying no
information is available raises `ntnu_no_info_error`. robots.txt asks for a
10-second crawl delay (`request_delay` in the config).

**UiO.** UiO publishes only the latest version of each course plan: the base
URL always returns the current plan and older versions cannot be reached.
Semester URLs (`/h24/`, `/v25/`) hold logistics only (teachers, timetable, exam
dates), not the plan, so they are not used. Data should be filtered to the
current year. The URL needs faculty/department slugs derived from
`Avdelingsnavn`, via a hard-coded mapping in `add_course_url_uio()`. Pattern:
`https://www.uio.no/studier/emner/{faculty}/{inst}/{CODE}/`.

**HiOF.** Courses before autumn 2021 use a different URL structure (switch in
`add_course_url_hiof()`); the config selector lists fallbacks for the old and
new page layouts.

**USN.** The URL holds a version number that metadata cannot give:
`https://www.usn.no/studier/studie-og-emneplaner/#/emne/{CODE}_{VERSION}_{YEAR}_{SEMESTER}`.
Each version (1, 2, 3, …) is a revision valid for a range of years, and an
invalid version/year combination silently shows another page without changing
the URL. `resolve_urls_usn_batch()` therefore renders each candidate in Chrome
(`rvest::read_html_live()`, hash routing) and checks that the displayed
"Undervisningsstart" year matches. It tries versions 1-5 and stops early when
the course code is missing from the page (no such version) or version 1 starts
after the requested year (course did not exist yet); NA means no version exists
for that semester. The content is rendered inside Shadow DOM, which
`html_text()` cannot read; `read_usn_live_html(session)` walks the shadow roots
with JavaScript:

```{r}
#| eval: false
session <- rvest::read_html_live(url)
Sys.sleep(5)  # wait for JS rendering
content <- read_usn_live_html(session)
session$session$close()
```

The batch resolver reuses one Chrome session and navigates by changing
`window.location.hash`, which avoids a 2-3 s browser start per URL. HTML is
captured during resolution, so USN has no separate fetch step.

**UiT.** Historical plans need a document id:
`https://uit.no/utdanning/emner/emne?p_document_id={ID}`. The active page
(`/utdanning/aktivt/emne/{CODE}`) has a `<select>` listing every semester with
its document id (option text `{CODE}: H 2020` / `{CODE}: V 2021`), also for
discontinued courses. The same CSS selector works for active and historical
pages.

**Samas.** `noop` strategy: `extracted_text` is NA, since the plans are in Sámi.

## Key Functions Reference

| Function | File | Purpose |
|---|---|---|
| `harvest_institution(institution, courses, year, refetch)` | `R/harvest.R` | Harvest one institution with its configured strategy |
| `harvest_all(courses, year, refetch, institutions)` | `R/harvest.R` | Harvest all (or the given) institutions: the first harvest to `data/raw/html_{inst}.RDS`, later ones add `data/raw/harvests/{date}/` |
| `institution_from_code(code)` | `R/institution_config.R` | Institution short name for DBH institution codes |
| `get_institution_config(inst)` | `R/institution_config.R` | Config list for one institution |
| `add_course_id(dbh_df)` | `R/utils.R` | Unique id from institution, raw code, year, semester, status |
| `add_course_url(df)` | `R/add_course_url.R` | Institution-specific URL builders; NA where discovery is needed |
| `resolve_course_urls(df, checkpoint_path)` | `R/resolve_course_urls.R` | URL discovery (USN, UiT, hivolda) with checkpointing |
| `fetch_html_with_checkpoint(courses, checkpoint_path)` | `R/checkpoint.R` | Download HTML, skipping courses already in the checkpoint |
| `extract_fulltext_from_raw(df, config)` | `R/extract_fulltext.R` | `extracted_text` from the raw harvest, per strategy |
| `page_blocks(html, text, cfg)` | `R/blocks.R` | Read one page into a block table |
| `page_fulltext(blocks, config)` | `R/extract_fulltext.R` | A page's `extracted_text` from its blocks |
| `read_harvest(files, config)` | `R/pipeline.R` | One institution's raw files combined (`harvest_files()`); current sites matched by course code and academic year |
| `harvested_rows(institutions)` | `R/pipeline.R` | `read_harvest()` joined with `data/interim/extracted_text.RDS` (audit scripts) |
| `finalize_release(tag)`, `frozen_changes()` | `R/release.R` | Lock a release's raw files; list changes to it (target `frozen_check`) |
| `release_data(tag, dest)` | `R/release.R` | Copy the published files, `methods.md`, a manifest and section coverage to the coding project |
| `plan_gaps(offerings, fetch_status)` | `R/pipeline.R` | Course-years without a plan, with the reason (target `gaps`) |
| `validate_courses(df, stage)` | `R/utils.R` | Required columns at `"initial"`, `"with_url"`, `"with_html"` |
| `anonymize_text(institution, text)` | `R/anonymize.R` | PII and admin-date removal for `course_plan` and sections |
| `normalize_plan_text(course_plan)` | `R/normalize_plan_text.R` | Lossy normalization for dedup hashing |
| `deduplicate_plans(df)` | `R/deduplicate_plans.R` | Content hashes → `plans` and `courses` with `plan_content_id` |
| `page_sections(blocks, text, cfg)` | `R/extract_sections.R` | A page's sections from its blocks |
| `extract_sections(config, html, extracted_text, course_id)` | `R/extract_sections.R` | `page_sections()` for many pages |

## Troubleshooting

**URLs look wrong?**
- Check the institution's builder in `R/add_course_url.R`
- Print a few: `courses |> filter(institution == "inst") |> add_course_url() |> select(url) |> head()`

**HTML download fails?**
- Check if the website is accessible in a browser
- Look at `html_error` for error messages
- Some institutions rate-limit or block automated requests
- For NTNU, check whether the page says no information is available

**Extracted text is empty or wrong?**
- Verify the CSS selector with browser dev tools on a real course page
- Update the selector in `R/institution_config.R` if the website changed, then `targets::tar_make()` (no new harvest needed)
- Read one page into blocks and look at them: `page_blocks(html, NA, .block_cfg(get_institution_config("inst")))`
- Some pages have different structures for different years

**Content missing from JavaScript-rendered pages?**
- Shadow DOM content is invisible to `html_text()`; see USN above
- `session$session$Runtime$evaluate("...")` runs JavaScript in a live session
- `session$view()` opens the browser to see what is rendered

**Checkpoint file is huge?**
- This is normal - HTML is large
- Checkpoint files are in `.gitignore`; deleting one makes the next run fetch again
  the offerings that are not yet in a raw file (never the ones that are)

**"raw files are not written twice"?**
- A harvest of the same institution already ran today; the raw store is
  append-only (#296). Run it another day, or, before the release is finalized,
  remove that day's file deliberately

**"offerings in more than one raw file"?**
- Two raw files of an institution hold the same `course_id`; a file was copied
  into `data/raw/` by hand. Remove the copy

## File Organization

```
├── _targets.R                 # Post-harvest pipeline: targets::tar_make()
├── methods.qmd                # Methods choices for articles (rendered to methods.md)
├── renv.lock                  # Pinned package versions (renv::restore())
├── .github/workflows/tests.yml # Tests on GitHub Actions
├── R/
│   ├── harvest.R              # Entry points: harvest_institution(), harvest_all()
│   ├── harvest_strategies.R   # Strategy implementations
│   ├── institution_config.R   # Institution registry (strategy, selectors, overrides, section_*)
│   ├── utils.R                # Helpers (data paths, add_course_id, validation, normalization)
│   ├── add_course_url.R       # URL generation logic
│   ├── resolve_course_urls.R  # URL discovery for USN, UiT, hivolda
│   ├── fetch_html_cols.R      # HTML downloading (httr2)
│   ├── extract_fulltext.R     # Config-driven text extraction
│   ├── checkpoint.R           # Checkpoint management
│   ├── anonymize.R            # PII removal: anonymize_text() for course_plan and sections
│   ├── normalize_plan_text.R  # Lossy normalization for dedup hashing
│   ├── deduplicate_plans.R    # Groups identical plans by content hash
│   ├── section_heading_map.R  # Heading → section patterns (incl. ".drop")
│   ├── extract_sections.R     # Section extraction strategies + cleanup
│   ├── pipeline.R             # Steps of the {targets} pipeline (_targets.R)
│   ├── pipeline_metrics.R     # Regression snapshot: check_pipeline_metrics()
│   ├── release.R              # release_data(), finalize_release(), frozen_changes()
│   └── audit/                # Audit harness for /audit-institutions
├── app/
│   ├── course_browser/        # Shiny concordance browser; build_data.R → data/ (see its README)
│   └── course_browser_ojs/    # Static Observable JS browser; build_data.R → data/ (see its README)
├── data/                      # README "Data Files: Published and Internal"
│   ├── input/courses.RDS      # DBH course list, the pipeline input (in git)
│   ├── raw/                   # Harvest: html_{inst}.RDS, harvests/{date}/, checkpoint/ (not in git)
│   ├── interim/               # Rebuilt text with personal data (not in git)
│   ├── processed/             # Anonymized data files, can be shared (not in git)
│   ├── releases/              # Finalized releases' data (not in git)
│   ├── backup/                # Earlier harvests, not read (not in git)
│   ├── audit/                 # Audit findings and reports
│   └── data_notes.qmd         # Data quality notes per institution
├── tests/
│   ├── testthat/              # Rscript -e 'testthat::test_dir("tests/testthat")'
│   └── snapshots/             # pipeline_metrics.csv; raw_manifest.csv once a release is finalized
└── data-raw/
    └── courses.R              # script that creates data/input/courses.RDS
```

## Need Help?

Look at the existing institution examples, but be quick to contact me, also! 🤩
