---
title: TEPS Course Content Harvest - User Guide
format: md
---

```{r}
#| echo: false
#| output: false
library(tidyverse)
```

## Overview

This project harvests course descriptions from Norwegian teacher education institutions. It takes course codes, years, and semesters as input and produces structured data containing URLs, HTML, and extracted text from course webpages.

**Input:** A tibble as output by `rdbhapi` with course metadata (institution, course code, year, semester)

**Output:** The same tibble with added course URL, raw HTML, and extracted text

### Pipeline Stages

| Stage | Code | Output |
|---|---|---|
| 1. Course id `{institution}_{Emnekode_raw}_{year}_{semester}_{status}` | `add_course_id()` (`R/utils.R`) | `course_id` |
| 2. URL from metadata (institution-specific builders; NA where the URL must be discovered) | `add_course_url()` (`R/add_course_url.R`) | `url` |
| 3. URL discovery (USN, UiT, hivolda; optional) | `resolve_course_urls()` (`R/resolve_course_urls.R`) | `url`, checkpoint `data/raw/checkpoint/urls_{inst}.RDS` |
| 4. Fetch HTML with checkpointing | `fetch_html_with_checkpoint()` (`R/checkpoint.R`, `R/fetch_html_cols.R`) | `html`, `html_success`, `html_error` |
| 5. Extract text (CSS selector, nla JSON, USN cleanup) | `extract_fulltext_from_raw()` (`R/extract_fulltext.R`) | `data/raw/html_{inst}.RDS` (raw harvest) |
| 6. Rebuild the text from the stored HTML | `institution_fulltext()` (`R/pipeline.R`) | `extracted_text.RDS` |
| 7. Anonymize and deduplicate | `institution_plans()` | `course_plans.RDS`, `course_offerings*.RDS` |
| 8. Split each plan into sections | `institution_sections()` | `plan_sections.RDS` |

Stages 1-5 are run per institution by `harvest_institution()`, which dispatches
to a strategy in `R/harvest_strategies.R` (`standard`, `url_discovery`,
`shadow_dom`, `html_pdf_discovery`, `pdf_split`, `json_extract`, `noop`).
`R/institution_config.R` is the single source of truth for each institution:
strategy, CSS selector, `selector_mode`, `year_in_url`, pre/post functions,
fetch overrides and the `section_*` fields. Stages 6-8 and everything after
them are a {targets} pipeline (see "Rebuilding Derived Data").

`data/raw/html_{inst}.RDS` is the raw harvest and only harvesting writes it. The
steps after it rebuild everything from it with the current code, so a changed
selector or post function needs `targets::tar_make()`, not a new harvest. The `extracted_text` saved with the harvest is not used
downstream, except for plans that came from a PDF (uis archive plans,
steiner): the PDF is not kept, so that text is the raw data.

## Quick Start: Running the Pipeline

The main entry points are in `R/harvest.R`:

```{r}
#| eval: false

# Load all pipeline functions
source("R/utils.R")
source("R/add_course_url.R")
source("R/resolve_course_urls.R")
source("R/fetch_html_cols.R")
source("R/extract_fulltext.R")
source("R/institution_config.R")
source("R/checkpoint.R")
source("R/harvest_strategies.R")
source("R/harvest.R")

# Harvest a single institution
courses <- readRDS("data/input/courses.RDS")
result <- harvest_institution("hivolda", courses)
saveRDS(result, "data/raw/html_hivolda.RDS")

# Only one year, or ignore the checkpoints and fetch again
result <- harvest_institution("oslomet", courses, year = 2025)
result <- harvest_institution("ntnu", courses, refetch = TRUE)

# Or harvest all institutions at once (saves data/raw/html_{inst}.RDS)
harvest_all()
```

The source order matters: `R/institution_config.R` refers to functions defined
in `R/fetch_html_cols.R` and `R/extract_fulltext.R`.

### What Happens Under the Hood

1. **`get_institution_config()`**: Looks up strategy, CSS selectors, and overrides
2. **`apply_year_filter()`**: Filters to relevant years based on config
3. **`add_course_id()`**: Creates unique identifiers for each course
4. **`add_course_url()`**: Generates the correct URL for each course
5. **Strategy dispatch**: Routes to the right harvesting strategy (standard, URL discovery, etc.)
6. **`ensure_output_columns()`**: Guarantees uniform output shape

### About Checkpointing

The pipeline uses **checkpointing** to avoid re-downloading data. If the script stops or crashes:

- Already-downloaded HTML is saved in `data/raw/checkpoint/html_{institution}.RDS` (`course_id`, `html`, `html_success`, `html_error`)
- Re-running the script fetches only courses not in the checkpoint (anti-join by `course_id`)
- This saves time and is polite to institutional servers

### Rebuilding Derived Data

Everything after the harvest is a {targets} pipeline: `_targets.R` lists the
steps, `R/pipeline.R` holds their functions. Run it after a harvest or after
changing code or config:

```{r}
#| eval: false
targets::tar_make()               # rebuild whatever is outdated
targets::tar_outdated()           # what would be rebuilt, without building
targets::tar_read(metrics_check)  # changes against the metrics snapshot
targets::tar_read(unmapped)       # headings the section extractor could not map
targets::tar_read(privacy_check)  # personal data found in data/processed/
```

{targets} keeps each step's result in `_targets/` (gitignored) together with a
hash of its inputs and of the code it calls, and reruns a step only when one of
those changed. The steps per institution (fulltext, plans, sections, unmapped
headings) run once per institution: a new `data/raw/html_uib.RDS`, or a change to
uib's entry in `R/institution_config.R`, rebuilds only uib, while a change to
shared code (`R/anonymize.R`, `R/section_heading_map.R`,
`R/extract_sections.R`) reruns that step for every institution. The pipeline
writes the data files in `data/interim/` and `data/processed/` (see "Data Files: Published and Internal"),
`app/course_browser/data/browser_data.RDS`, the OJS Parquet files and `data/data_notes.md`. The
harvest is not part of it.

The steps run on 4 local worker processes ({crew}, set in `tar_option_set()`
in `_targets.R`), several institutions at a time. A full build takes about 19
minutes; the floor is the slowest single institution's sections (about 8
minutes). To debug a step with `browser()`, run in the current session instead:
`targets::tar_make(callr_function = NULL, use_crew = FALSE)`.

The pipeline ends by comparing the built data with a snapshot of
per-institution and per-section counts and median text lengths
(`R/pipeline_metrics.R`, `tests/snapshots/pipeline_metrics.csv`). Changes
beyond tolerance show as a warning in `tar_make()` and make
`tests/testthat/test-pipeline-metrics.R` fail. When a change is intended,
update the snapshot and commit it together with the change:

```{r}
#| eval: false
source("R/pipeline_metrics.R")
check_pipeline_metrics(update = TRUE)
```

Per-institution prose notes are edited directly in `data/data_notes.qmd`.

### Packages and Tests

Package versions are pinned with renv: `renv.lock` records R 4.6.1 and every
package the code uses, and R started in this folder loads them from the
project library in `renv/` (activated by `.Rprofile`). On a new machine,
`renv::restore()` installs them. After adding a package, record it with
`renv::snapshot()` and commit `renv.lock`.

The tests run with `testthat::test_dir("tests/testthat")`, and on GitHub
Actions for every push and pull request to main
(`.github/workflows/tests.yml`, packages from `renv.lock`). Tests that need
the harvested or built data (only `data/input/` is in git), a browser or external URLs
skip themselves there.

## Adding a New Institution

To add support for a new institution, you need to modify **two files**. In
Claude Code, the `/add-institution` skill walks through the same steps.

### 1. Add config entry to `R/institution_config.R`

```{r}
#| eval: false

# Add to the institution_configs list:
newuni = list(
  code = "1234",
  strategy = "standard",          # or url_discovery, shadow_dom, etc.
  selector = ".main-content",     # CSS selector for course plan content
  selector_mode = "single",       # "single" or "multi"
  year_in_url = TRUE
)
```

**How to find CSS selectors:**

1. Open a course page in your browser
2. Right-click on the course description text → "Inspect"
3. Look for a `class` or `id` attribute that wraps the content
4. Use the SelectorGadget tool: https://rvest.tidyverse.org/articles/selectorgadget.html
5. Test your selector to make sure it captures all course text

Use `selector_mode = "multi"` when the plan is spread over several elements
(nord, uib, uis, uit do this for accordions and sections).

### 2. Add URL builder to `R/add_course_url.R`

Add a case to `case_match()` and create a URL-building function:

```{r}
#| eval: false

# In add_course_url(), add:
"newuni" ~ add_course_url_newuni(Emnekode, Årstall, Semesternavn),

# Create a helper function for your institution
add_course_url_newuni <- function(course_code, year, semester) {
  semester <- case_match(semester, "Vår" ~ "spring", "Høst" ~ "autumn")
  glue::glue("https://www.newuni.no/courses/{year}/{semester}/{tolower(course_code)}")
}
```

### 3. Test Your Changes

```{r}
#| eval: false

# Load pipeline and test
courses <- readRDS("data/input/courses.RDS")
result <- harvest_institution("newuni", courses, year = 2025)

# Inspect results
result |> select(Emnekode, url, html_success, extracted_text) |> head()
result$extracted_text[1]  # Inspect first result
```

Expand a little bit at a time, for example by year. Add more years as the pipeline works.

For standard institutions no changes to `R/extract_fulltext.R` or
`R/harvest_strategies.R` are needed. Sites that need a browser (Shadow DOM),
PDF splitting or URL discovery need a strategy function in
`R/harvest_strategies.R`.

## Post-Harvest: Anonymization and Deduplication

The pipeline anonymizes and deduplicates the course plans in three stages:

1. **Anonymize** (`anonymize_text()`): Removes PII (teacher names, emails, phone numbers, staff lists "Name (Role)", signature lines "Name, dekan"), dates, seasons, and administrative year references ("Opprettet 2020", "2023/2024") from `extracted_text`, producing a readable `course_plan` column. Content years (e.g., "etter 1945", "NOU 2015:2") are preserved. Institution-specific handlers (`.anon_*()`) run first, then the generic cleanup (`.anon_generic()`).
2. **Normalize** (`normalize_plan_text()`): Applies lossy transforms (lowercasing, heading synonyms, blanket year removal, whitespace squishing) on `course_plan` for content hashing
3. **Deduplicate** (`deduplicate_plans()`): Groups identical normalized texts under a shared `plan_content_id`

**Output columns:**

| Column | Description |
|--------|-------------|
| `course_plan` | Anonymized, readable text (primary column for consumers) |
| `extracted_text` | Raw extracted text (kept for debugging) |
| `course_plan_normalized` | Lossy normalized text (internal, for hashing) |
| `plan_content_id` | SHA-256 hash of `course_plan_normalized` |

**Output files:**

- `data/processed/course_offerings.RDS` — published slim dataset: course rows with DBH metadata + `plan_content_id` FK (no url, no text)
- `data/interim/course_offerings_full.RDS` — internal working file: same rows plus `url`, `extracted_text`, `course_plan`, `course_plan_normalized`; used by the course_browser app
- `data/processed/course_plans.RDS` — one row per unique plan per course code per institution, with the offering its text comes from (`source_course_id`)

## Post-Harvest: Section Extraction

The pipeline splits each course plan into its parts and writes
`data/processed/plan_sections.RDS` with one row per plan and section
(`plan_content_id`, `institution`, `Emnekode`, `source_course_id`, `section`,
`text`), keyed like `course_plans.RDS`. A plan's sections are cut from the page
of `source_course_id`, the offering whose text the plan keeps, so they match
its `course_plan`. The seven sections are
`course_content`, `learning_outcomes`, `teaching_methods`, `assessment`,
`coursework_requirements`, `prerequisites` and `reading_list`. Section text is
anonymized with the same `anonymize_text()` as `course_plan`: sections are cut
from the raw `html`/`extracted_text`, so this step must keep anonymizing.
Admission text, exam logistics and placeholder rows such as "Se fagplanen." are
left out.

`tar_read(metrics)` has the number of plans with each section per
institution, and `tar_read(unmapped)` the headings the extractor could not map. To map a new heading, add a pattern to
`R/section_heading_map.R`; how each institution is split is set by the
`section_*` fields in `R/institution_config.R`.

### Strategies

`extract_sections()` (`R/extract_sections.R`) dispatches on `section_strategy`:

| Strategy | Institutions | How it splits |
|---|---|---|
| `html_headings` | oslomet, uia, ntnu, inn, hiof, hvl, nih, uio, uis, uit, nmbu | DOM walk; a heading (`section_heading_level`, or `section_heading_selector`, e.g. ntnu `"h2, h3"` for its "Eksamen" block) starts a section. Falls back to `text_split` when it finds < 3 sections |
| `html_fields` | hivolda | `div.field-<name>` containers mapped to sections by `section_fields` |
| `details_mf` | mf | `<details><summary>` accordions + the untitled intro block (`section_intro_selector`) as course_content |
| `details_uib` | uib | `<details><summary>` accordions + top-level `h2` |
| `accordion_nord` | nord | `div.ac` accordion trigger/panel pairs |
| `json_nla` | nla | Titles in the embedded EmneplanPage JSON |
| `text_split` | usn, steiner (+ fallback, e.g. uis PDF plans) | Heading-shaped lines in `extracted_text`; skips a table of contents ("Innholdsfortegnelse", usn); inside a reading list opened by a whole heading only a whole heading switches section (book titles) |
| `noop` | samas | — |

Other `section_*` config fields:

- `section_selector`: container for section extraction when the fulltext
  `selector` is a multi-element selector (`html_element()` would only take its
  first match; uis needs `#block-page-content`).
- `section_subheading_selector`: elements inside a section that switch to
  another section (uio `"h3, h4, p"`; `"p"` for uia, oslomet, hiof, hvl, nmbu,
  mf). A `<p>` counts if its whole text (minus a trailing colon) equals a
  heading pattern, or if its leading `<em>`/`<strong>` run or its first or
  last `<br>`-separated line does (uia `<p><em>Faget i praksis</em>I løpet
  …</p>`). A whole-bold `<p>` that names no section is a group label: it ends
  a sub-section and returns to the parent. Sub-headings act only under a
  mapped heading (oslomet's programme "Fagplan" block stays out); one naming
  the section already open ("Kunnskap") stays as content. A `<p>` in a list
  item is skipped unless that `<li>` holds a section heading (oslomet's
  accordion). An unmapped `h3` ("Karakterskala") hands its text back to the
  parent section, keeping the heading as its first line. A colon-ended
  lead-in naming a coursework gate ("… følgende obligatoriske aktiviteter:")
  starts coursework_requirements.
- `section_text_header`: regex for a title + metadata block at the top of
  `extracted_text` (uis PDFs: "Emnekode:", "Tilbys av:"); `text_split` skips
  it and files the untitled paragraph after it as course_content.
- `section_inline_coursework`: move "Arbeidskrav (AK): …" / "Obligatorisk
  deltakelse …" lines from assessment to coursework_requirements (nord).

### Heading Map and Cleanup

`match_heading_to_section()` (`R/section_heading_map.R`) checks exact equality
against every pattern first, then substring patterns in table order (first hit
wins; rows with `exact = TRUE` only match whole headings). `text_split` passes
`word_start = TRUE` so "elevkunnskap" does not match "kunnskap", and only
accepts heading-shaped lines (capitalised, ≤ 8 words, no digits, no "Label:
value", no closing full stop). Patterns mapped to `".drop"` end the current
section and their text is discarded: admission headings ("Opptak til emnet",
"Opptakskrav", "Hvem kan ta dette emnet?") and exam logistics ("Mer om eksamen
ved UiO", "Hjelpemidler", "Sensorordning", resit headings such as "Ny/utsatt
eksamen"). Exam language and grading scale stay in assessment.

HTML is parsed by `.read_doc()`, which drops `script`, `style`, `select` and
`label` (ntnu script text, uib semester picker); `json_nla` parses the page
itself because its data is in a `<script>`.

`.clean_sections()` removes `.drop` rows, strips notices and page widgets from
assessment/coursework (`.section_noise`: plagiarism and ChatGPT/COVID notices,
uib banner and footer, flattened exam-table headers, …), removes admission
sentences from prerequisites (`.strip_admission_lines()`), drops
placeholder-only rows (`.placeholder_phrases`: "Ingen", "Se fagplanen.", "-",
Leganto pointers, "Oppgis senere.", "… ikke publisert ennå"), and drops a first
line that only repeats the section heading (but keeps learning-outcome group
labels such as "Kunnskap").

## Auditing a Pipeline Step

The `/audit-institutions <sections|fulltext|anonymization> [inst ...]` skill
(Claude Code) checks a pipeline step for every institution with one review
agent per institution. R scripts build a review packet per institution
(`R/audit/prepare_{check}.R`; for sections after the deterministic pre-pass
`R/audit/qa_sections.R`), the agents write findings to
`data/audit/{check}/findings/{inst}.json`, and `R/audit/aggregate.R` verifies
them (course ids and verbatim quotes must be in the packet) and writes a ranked
cross-institution report. Details: `.claude/skills/audit-institutions/SKILL.md`.

## Data Files: Published and Internal

Files that hold raw page text (`html`, `extracted_text`) contain staff names,
e-mail addresses and phone numbers and are never published. Everything that is
shared is built from the anonymized text (`anonymize_text()`). The data are
kept in one folder per stage, so the folder says what may be shared:

| Folder | Holds | Written by | In git |
|---|---|---|---|
| `data/input/` | the DBH course list, the pipeline input | `data-raw/courses.R` | yes |
| `data/raw/` | the harvest, with personal data | harvesting only | no |
| `data/interim/` | text rebuilt from the harvest, with personal data; never shared | `targets::tar_make()` | no |
| `data/processed/` | anonymized data or data without text; can be shared | `targets::tar_make()` | no |

`data/processed/` may only hold text that went through `anonymize_text()`. The
pipeline checks this on every build: target `privacy_check` scans the files for
e-mail addresses, phone numbers, "Name (Role)" lines and "Name, dekan"
signatures and warns, and `tests/testthat/test-anonymize.R` fails, on any hit.
The repository is public.

| File | Contents | Personal data | Status |
|---|---|---|---|
| `data/input/courses.RDS` | DBH course metadata (pipeline input) | none | in git |
| `data/raw/html_{inst}.RDS`, `data/raw/checkpoint/` | raw harvest: `html` (+ `extracted_text` from harvest time) | yes (raw) | internal |
| `data/interim/extracted_text.RDS` | `extracted_text` rebuilt from the raw harvest | yes (raw) | internal |
| `data/interim/course_offerings_full.RDS` | offerings + `url`, `extracted_text`, `course_plan` | yes (`extracted_text`) | internal |
| `data/processed/course_offerings.RDS` | DBH metadata + `plan_content_id`, no text | none | published |
| `data/processed/course_plans.RDS` | anonymized `course_plan` (+ `course_plan_normalized`) | anonymized | published |
| `data/processed/plan_sections.RDS` | anonymized section `text` per plan | anonymized | publishable |
| `app/course_browser/data/browser_data.RDS` | course_browser payload: plans, offering metadata, sections | anonymized (no `extracted_text`) | internal (app) |
| `app/course_browser_ojs/data/*.parquet` | anonymized `course_plan` + slim offering metadata | anonymized | published with the OJS page (build artifact) |
| `data/audit/` | audit findings (quotes from anonymized text) | staff names redacted | in git |

The scan catches text that skipped the anonymizer, not names the anonymizer
misses; the anonymization audit (`/audit-institutions anonymization`) checks
that per institution.

## Data Structure

### Input Data (`data/input/courses.RDS`)

The courses dataset contains:

```{r}
courses <- readRDS("data/input/courses.RDS")
courses |> slice(1:2)
```

Key columns:
- `institution`: Short code (e.g., "oslomet", "uia")
- `Emnekode_raw`: Original course code from DBH (used in `course_id`)
- `Emnekode`: Course code with the trailing version number removed (`canon_remove_trailing_num()`: "ABC123-1" → "ABC123")
- `Årstall`: Year
- `Semesternavn`: Semester name ("Vår" or "Høst"; `canon_semester_name()` maps Vår/Høst/Sommer to spring/autumn/summer)
- `Status`: Course status (1=Active, 2=New, 3=Discontinued, 4=Discontinued but exam offered)

DBH lists most courses under both semesters of a year, also when they are
taught in one. Where pages are semester-specific, about half the rows therefore
have no plan by design; see "Semester registration in DBH" in
`data/data_notes.qmd` before reading row-level success rates.

### Output Data Structure

After processing, you'll have:

```{r}
#| echo: false
output <- tribble(
  ~course_id, ~url, ~html, ~html_success, ~extracted_text, ~course_plan,
  "oslomet_ABC123_2024_autumn_1", "https://student.oslomet.no/...", "<html>...</html>", TRUE, "ABC123 Course Description...", "ABC123 Course Description...",
  "oslomet_XYZ456_2024_spring_1", "https://student.oslomet.no/...", "<html>...</html>", TRUE, "XYZ456 Another course...", "XYZ456 Another course..."
)
output
```

- `course_plan` is the anonymized version of `extracted_text` (no names, emails, dates, or administrative years). Content years like historical references are preserved. Use this column for analysis.

## Institution-Specific Notes

**NORD.** The URL needs Norwegian characters in the semester parameter
(`HØST`/`VÅR`); ASCII `HOEST` falls back to a generic "Gjeldende
emnebeskrivelse" page without year-specific content. The site maps each
semester to its academic year (`VÅR&year=2023` gives the 2022/23 plan). Pattern:
`https://www.nord.no/studier/emner/{code}?year={year}&semester={HØST|VÅR}`.

**NTNU.** The URL has the year but not the semester. A page saying no
information is available raises `ntnu_no_info_error`. robots.txt asks for a
10-second crawl delay (`request_delay` in the config).

**UiO.** UiO publishes only the latest version of each course plan: the base
URL always returns the current plan and older versions cannot be reached.
Semester URLs (`/h24/`, `/v25/`) hold logistics only (teachers, timetable, exam
dates), not the plan, so they are not used. Data should be filtered to the
current year. The URL needs faculty/department slugs derived from
`Avdelingsnavn`, via a hard-coded mapping in `add_course_url_uio()`. Pattern:
`https://www.uio.no/studier/emner/{faculty}/{inst}/{CODE}/`.

**HiOF.** Courses before autumn 2021 use a different URL structure (switch in
`add_course_url_hiof()`); the config selector lists fallbacks for the old and
new page layouts.

**USN.** The URL holds a version number that metadata cannot give:
`https://www.usn.no/studier/studie-og-emneplaner/#/emne/{CODE}_{VERSION}_{YEAR}_{SEMESTER}`.
Each version (1, 2, 3, …) is a revision valid for a range of years, and an
invalid version/year combination silently shows another page without changing
the URL. `resolve_urls_usn_batch()` therefore renders each candidate in Chrome
(`rvest::read_html_live()`, hash routing) and checks that the displayed
"Undervisningsstart" year matches. It tries versions 1-5 and stops early when
the course code is missing from the page (no such version) or version 1 starts
after the requested year (course did not exist yet); NA means no version exists
for that semester. The content is rendered inside Shadow DOM, which
`html_text()` cannot read; `read_usn_live_html(session)` walks the shadow roots
with JavaScript:

```{r}
#| eval: false
session <- rvest::read_html_live(url)
Sys.sleep(5)  # wait for JS rendering
content <- read_usn_live_html(session)
session$session$close()
```

The batch resolver reuses one Chrome session and navigates by changing
`window.location.hash`, which avoids a 2-3 s browser start per URL. HTML is
captured during resolution, so USN has no separate fetch step.

**UiT.** Historical plans need a document id:
`https://uit.no/utdanning/emner/emne?p_document_id={ID}`. The active page
(`/utdanning/aktivt/emne/{CODE}`) has a `<select>` listing every semester with
its document id (option text `{CODE}: H 2020` / `{CODE}: V 2021`), also for
discontinued courses. The same CSS selector works for active and historical
pages.

**Samas.** `noop` strategy: `extracted_text` is NA, since the plans are in Sámi.

## Key Functions Reference

| Function | File | Purpose |
|---|---|---|
| `harvest_institution(institution, courses, year, refetch)` | `R/harvest.R` | Harvest one institution with its configured strategy |
| `harvest_all(courses, year, refetch, institutions)` | `R/harvest.R` | Harvest all (or the given) institutions, save `data/raw/html_{inst}.RDS` |
| `get_institution_config(inst)` | `R/institution_config.R` | Config list for one institution |
| `add_course_id(dbh_df)` | `R/utils.R` | Unique id from institution, raw code, year, semester, status |
| `add_course_url(df)` | `R/add_course_url.R` | Institution-specific URL builders; NA where discovery is needed |
| `resolve_course_urls(df, checkpoint_path)` | `R/resolve_course_urls.R` | URL discovery (USN, UiT, hivolda) with checkpointing |
| `fetch_html_with_checkpoint(courses, checkpoint_path)` | `R/checkpoint.R` | Download HTML, skipping courses already in the checkpoint |
| `extract_fulltext_css(html, selector, mode, pre_fn, post_fn)` | `R/extract_fulltext.R` | Config-driven CSS text extraction |
| `extract_fulltext_from_raw(df, config)` | `R/extract_fulltext.R` | `extracted_text` from the raw harvest, per strategy |
| `read_harvest(institutions)` | `R/extract_fulltext.R` | Raw harvest joined with `data/interim/extracted_text.RDS` |
| `validate_courses(df, stage)` | `R/utils.R` | Required columns at `"initial"`, `"with_url"`, `"with_html"` |
| `anonymize_text(institution, text)` | `R/anonymize.R` | PII and admin-date removal for `course_plan` and sections |
| `normalize_plan_text(course_plan)` | `R/normalize_plan_text.R` | Lossy normalization for dedup hashing |
| `deduplicate_plans(df)` | `R/deduplicate_plans.R` | Content hashes → `plans` and `courses` with `plan_content_id` |
| `extract_sections(institution, html, extracted_text, course_id)` | `R/extract_sections.R` | Split course pages into the seven sections |

## Troubleshooting

**URLs look wrong?**
- Check the institution's builder in `R/add_course_url.R`
- Print a few: `courses |> filter(institution == "inst") |> add_course_url() |> select(url) |> head()`

**HTML download fails?**
- Check if the website is accessible in a browser
- Look at `html_error` for error messages
- Some institutions rate-limit or block automated requests
- For NTNU, check whether the page says no information is available

**Extracted text is empty or wrong?**
- Verify the CSS selector with browser dev tools on a real course page
- Update the selector in `R/institution_config.R` if the website changed, then `targets::tar_make()` (no new harvest needed)
- Check whether the institution needs `selector_mode = "multi"`
- Some pages have different structures for different years

**Content missing from JavaScript-rendered pages?**
- Shadow DOM content is invisible to `html_text()`; see USN above
- `session$session$Runtime$evaluate("...")` runs JavaScript in a live session
- `session$view()` opens the browser to see what is rendered

**Checkpoint file is huge?**
- This is normal - HTML is large
- Checkpoint files are in `.gitignore`; deleting one makes the next run fetch again

## File Organization

```
├── _targets.R                 # Post-harvest pipeline: targets::tar_make()
├── renv.lock                  # Pinned package versions (renv::restore())
├── .github/workflows/tests.yml # Tests on GitHub Actions
├── R/
│   ├── harvest.R              # Entry points: harvest_institution(), harvest_all()
│   ├── harvest_strategies.R   # Strategy implementations
│   ├── institution_config.R   # Institution registry (strategy, selectors, overrides, section_*)
│   ├── utils.R                # Helpers (data paths, add_course_id, validation, normalization)
│   ├── add_course_url.R       # URL generation logic
│   ├── resolve_course_urls.R  # URL discovery for USN, UiT, hivolda
│   ├── fetch_html_cols.R      # HTML downloading (httr2)
│   ├── extract_fulltext.R     # Config-driven text extraction
│   ├── checkpoint.R           # Checkpoint management
│   ├── anonymize.R            # PII removal: anonymize_text() for course_plan and sections
│   ├── normalize_plan_text.R  # Lossy normalization for dedup hashing
│   ├── deduplicate_plans.R    # Groups identical plans by content hash
│   ├── section_heading_map.R  # Heading → section patterns (incl. ".drop")
│   ├── extract_sections.R     # Section extraction strategies + cleanup
│   ├── pipeline.R             # Steps of the {targets} pipeline (_targets.R)
│   ├── pipeline_metrics.R     # Regression snapshot: check_pipeline_metrics()
│   └── audit/                # Audit harness for /audit-institutions
├── app/
│   ├── course_browser/        # Shiny concordance browser; build_data.R → data/ (see its README)
│   └── course_browser_ojs/    # Static Observable JS browser; build_data.R → data/ (see its README)
├── data/                      # README "Data Files: Published and Internal"
│   ├── input/courses.RDS      # DBH course list, the pipeline input (in git)
│   ├── raw/                   # Harvest: html_{inst}.RDS, checkpoint/ (not in git)
│   ├── interim/               # Rebuilt text with personal data (not in git)
│   ├── processed/             # Anonymized data files, can be shared (not in git)
│   ├── audit/                 # Audit findings and reports
│   └── data_notes.qmd         # Data quality notes per institution
├── tests/
│   ├── testthat/              # Rscript -e 'testthat::test_dir("tests/testthat")'
│   └── snapshots/             # pipeline_metrics.csv (regression snapshot)
└── data-raw/
    └── courses.R              # script that creates data/input/courses.RDS
```

## Need Help?

Look at the existing institution examples, but be quick to contact me, also! 🤩
