---
title: Specification of data harvest for TEPS Course Content module
format: md
---

```{r}
#| echo: false
#| output: false
library(tidyverse)
library(openxlsx2)
```


The input are the institution, course code, year and semester:
```{r}
courses <- read_xlsx("data-raw/courses.xlsx")
courses |> slice(1:2)
```

This file should have at least one line for each teacher education institution with a five year integrated "Lektorprogram". These are `{r} courses$institution_short`. 

The output is a tibble with a course url, html, and full text from website, like this

```{r}
#| echo: false
output <- tribble(
  ~url, ~html, ~fulltekst,
  "https://student.oslomet.no/studier/-/studieinfo/emne/MGVM4100/2022/H%C3%98ST", "<head> html-koden [...]", "M5GEN100 Engelsk, emne ...",
  "https://[...]", "<head> annen html-kode", "teksten til en annen emnekode"
)
output
```

We want the entire pipeline to be computational, possibly consisting of these functions:

- `course_url(institution_short, course_code, year, semester)`, which ouputs the course_url.
- `extract_fulltext(institution_short, url)`, which outputs the full text of course information with ok formatting.

Ideally, the work is added to this repository.

Below are some suggested steps. When the work proceeds, you will have more knowledge of this than me, so feel free to suggest changes.

## 1. Create a file with one or more courses from each institution

See `data-raw/courses.xlsx` for a start.

## 2. Create `course_url` function

We would create using the `dplyr` function "case_match" and simple string pasting.

```{r}
courses |> 
  slice(1:3) |> 
  mutate(
    url = case_match(
      institution_short,
      "oslomet" ~ paste("www.oslomet.no/courses", course_code, year, semester, "index.html", sep = "/"),
      "uia" ~ paste("www.uia.no/course/info/", paste0(year, semester), course_code, "index.html", sep = "/")
    )
  )
```

(Koden over lager ikke riktige URLer. Jeg bare improviserte. 😸)

## 3. Retrieve all htmls

The `read_file` function can read urls!

## 4. Identify the css-selector corresponding to the full course text and collect them in a .xlsx

These are the steps I'm most unsure about. I don't know much about webscraping. I'm basing myself on the documentation of the R-package `rvest` and the relevant chapter of Rohan Alexander's open textbook, "Telling Stories with Data".

I envision having a function `scrape_course(institution_short, html)`

1. Get the selector gadget: https://rvest.tidyverse.org/articles/selectorgadget.html
2. Use it to find the css-selector corresponding to the full text of the course webpage.
3. Add code that parses this css-selector, for example to the `scrape_course` function.

That last step might be something like this. Only code for "OsloMet" is shown.:

```{r}
#| eval: false

scrape_course <- function(institution_short, html){
  if(institution_short == "oslomet"){
    fulltekst <- html |> 
      read_html() |> # the rest is from the 'rvest' package
      html_elements(".oslomet-margin-wrapper-top") |> # this is the css-selector on oslomet pages
      html_text2() |> #strip html code from html. Below is just to get nice formatting:
      str_replace_all("  ", " ") |> # remove excessive whitespace
      str_replace_all("[\r]", "") |> # remove carriage returns. Don't remember why I put it in brackets
      str_replace_all("^[:space:]+", "") |> # remove spaces at the beginning of lines
      str_replace_all("[\n]+", "\n\n") # replace any number of newlines with two newlines
    return(fulltekst)
  } 
}
```

