---
title: "Data Quality Notes"
format: gfm
execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
library(dplyr)

df    <- readRDS("processed/course_offerings.RDS")
plans <- readRDS("processed/course_plans.RDS")

summary_tbl <- df |>
  group_by(institution) |>
  summarise(
    Rows         = n(),
    Codes        = n_distinct(Emnekode_raw),
    year_min     = min(Årstall),
    year_max     = max(Årstall),
    `Extracted OK`= sum(has_extracted_text),
    has_plan_id  = sum(!is.na(plan_content_id)),
    `Median chars` = round(median(extracted_text_nchar[has_extracted_text], na.rm = TRUE)),
    `Unique plans` = n_distinct(plan_content_id, na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    Years     = ifelse(year_min == year_max, as.character(year_min), paste0(year_min, "-", year_max)),
    Rate      = sprintf("%.1f%%", `Extracted OK` / Rows * 100),
    `Dedup %` = sprintf("%.1f%%", (1 - `Unique plans` / has_plan_id) * 100)
  ) |>
  select(Institution = institution, Rows, Codes, Years,
         `Extracted OK`, Rate, `Median chars`, `Unique plans`, `Dedup %`)

total_rows     <- nrow(df)
total_text <- sum(df$has_extracted_text)
total_rate     <- sprintf("%.1f%%", total_text / total_rows * 100)
total_plans    <- nrow(plans)
single_year    <- sort(unique(df$institution[ave(df$Årstall, df$institution, FUN = function(y) length(unique(y))) == 1]))
```

Generated: `r Sys.Date()`

## Overview

```{r}
#| label: summary-table
knitr::kable(summary_tbl)
```

**Total**: `r total_rows` rows, `r total_text` with extracted text (`r total_rate`), `r total_plans` unique plans.

**Columns:**

- **Rows**: Total course-semester rows in harvested data (from DBH)
- **Codes**: Unique course codes (Emnekode_raw)
- **Extracted OK**: Rows with successfully extracted course plan text
- **Rate**: Extraction success rate (Extracted OK / Rows)
- **Median chars**: Median character count of extracted text
- **Unique plans**: Distinct course plans after normalization and deduplication
- **Dedup %**: Percentage of rows removed by deduplication (1 - unique/has_plan)

## Year coverage

Sites that show only the plan in force (`plan_years = "current"` in
`R/institution_config.R`) give, at each harvest, the plan of that academic
year only. Each harvest is kept, and an offering gets the plan from a harvest
made in its own academic year, or none (README "Sites that show only the
current plan"; #293). In this data the harvests are of 2026-04-04 (2025/26:
autumn 2025 offerings) and 2026-09-30 (2026/27: no DBH offerings yet), so
spring 2025 offerings (2024/25) have no plan at these sites. They are
`r paste(single_year, collapse = ", ")`.
The others have historical plans as far back as the site still serves them.
Share of offerings with a plan, by period:

```{r}
#| label: coverage-by-period
df |>
  mutate(Period = cut(Årstall, c(-Inf, 2014, 2017, 2019, 2021, 2023, Inf),
                      labels = c("–2014", "2015–17", "2018–19", "2020–21",
                                 "2022–23", "2024–"))) |>
  group_by(Institution = institution, Period) |>
  summarise(pct = sprintf("%.0f%%", mean(has_extracted_text) * 100), .groups = "drop") |>
  tidyr::pivot_wider(names_from = Period, values_from = pct, values_fill = "", names_sort = TRUE) |>
  knitr::kable()
```

## Semester registration in DBH

DBH lists most courses under both spring and autumn of a year, also when the
course is taught, and its plan published, in one semester only. How this shows
up depends on the website:

- **Semester-specific pages** (HiOF, Hivolda, NIH, NLA, UiA, USN): the other
  semester has no page (a 404, or no USN version), so about half of the rows
  lack text by design.
- **One page per course or year**: both rows get the same page, and
  deduplication collapses them.

The row-level **Rate** in the overview therefore understates coverage for the
first group. To compare institutions, count course-years (code × year) that have
a plan in at least one semester:

```{r}
#| label: semester-registration
course_years <- df |>
  group_by(institution, Emnekode_raw, Årstall) |>
  summarise(both = n_distinct(Semesternavn) == 2,
            n_plan = sum(!is.na(plan_content_id)), .groups = "drop")

course_years |>
  group_by(Institution = institution) |>
  summarise(
    `Course-years` = n(),
    `Both semesters in DBH` = sprintf("%.0f%%", mean(both) * 100),
    `Both reg., plan in one` = sum(both & n_plan == 1),
    `Both reg., plan in both` = sum(both & n_plan == 2),
    `Both reg., no plan` = sum(both & n_plan == 0),
    `Course-years with plan` = sprintf("%.0f%%", mean(n_plan > 0) * 100),
    .groups = "drop"
  ) |>
  left_join(select(summary_tbl, Institution, `Row rate` = Rate), by = "Institution") |>
  knitr::kable()
```

## Course-years without a plan

Why a course-year (code × year) has no plan in any semester, from
`data/interim/plan_gaps.RDS` (target `gaps`, `plan_gaps()` in
`R/pipeline.R`). **No URL**: the site has no page for that year, or URL
discovery found none (hivolda, uit, usn). **404**: the page was not found.
**Fetch error**: another error (ntnu's "no information" pages, uib).
**Page, no plan**: a page shell, a page that is not the plan, or a year
missing from NLA's JSON. **No page**: a current site without a harvest in
that year. **Between plans**: the course has a plan the year before and the
year after, so the gap is the likeliest to be a wrong URL or a missed page;
these are the ones to check by hand (`url_tried`, and `url_next_door`, the
page of an adjacent year that worked).

```{r}
#| label: plan-gaps
gaps <- readRDS("interim/plan_gaps.RDS")
gaps |>
  filter(!has_plan) |>
  group_by(Institution = institution) |>
  summarise(
    `Without plan` = n(),
    `404` = sum(grepl("404", reason)),
    `No URL` = sum(grepl("no URL", reason)),
    `Fetch error` = sum(grepl("fetch error", reason)),
    `Page, no plan` = sum(grepl("page, no plan", reason)),
    `No page` = sum(reason == "no page"),
    `Between plans` = sum(between_plans),
    .groups = "drop"
  ) |>
  knitr::kable()
```

To list the gaps between plans:
`readRDS("data/interim/plan_gaps.RDS") |> dplyr::filter(between_plans)`.

## Interpreting the dedup ratio

High dedup (>40%) is expected for current-year-only institutions where DBH registers courses for both semesters but only one plan page exists (see "Semester registration in DBH").

Low dedup (<10%) means most rows have genuinely different content, typically because plans change between years/versions (HiOF, USN) or each row is truly distinct (NIH, Steiner, UiO).

## Per-Institution Notes

Figures are in the tables above; the notes say why. Issue numbers refer to
chainlink.

---

### HiOF (Ostfold University College)

- Plans before autumn 2021 use another URL structure; `add_course_url_hiof()` switches by date, and the selector lists fallbacks for both page layouts
- Needs a browser-like user agent (`user_agent = "browser"`) to avoid 403s (#27)
- Most rows without a plan are the other semester of a course registered in both (see "Semester registration in DBH")
- Reading lists are part of the plan text; `.anon_hiof()` removes only the "Litteraturlista er sist oppdatert" line

---

### Hivolda (Volda University College)

- Semester-specific pages have numeric ids (e.g. `/emne/MGL5-10NO2B/12177`) that metadata cannot give; `resolve_urls_hivolda_batch()` reads them from the course's base page, matching "Haust" to "Høst" (#63, #79-#83)
- Rows without a plan are mostly semesters in which the course was not taught

---

### HVL (Western Norway University of Applied Sciences)

- Year in the URL. Soft-404 "course not found" pages are detected at fetch time (`fetch_html_cols_single_hvl()`) and stored as no HTML (#66)

---

### INN (Inland Norway University of Applied Sciences)

- No plans before 2022: INN's site starts in 2022, so the URL builder returns NA for earlier years (#26)
- Some pages are the course search page ("Emnesøket gjelder kun fra ...") instead of a plan; the anonymizer turns them into NA (#53)
- Some courses are published in both Norwegian and English (#52)
- Some 2022 pages show "Undervisningssemestre" for another year, and a few carry no plan; this is upstream, with no client-side fix (#123)

---

### MF (MF Norwegian School of Theology)

- Only the plan in force is published (`plan_years = "current"`; see "Year coverage"). Selector `main` (#25)
- `.anon_mf()` cuts from "Emneansvarlig" to the end (names, contact details, marketing)

---

### NIH (Norwegian School of Sport Sciences)

- Short year range. Most 404s are the other semester of a course registered in both (see "Semester registration in DBH"; #220)

---

### NLA (NLA University College)

- All DBH years (`plan_years = "page"`, #292): each course page embeds the plans of several academic years as JSON, for most courses only recent ones; the json block reader (`R/blocks.R`) takes the year of the row (spring 2025 → 2024-2025, autumn 2025 → 2025-2026). A row with a page but no plan is an academic year missing from that JSON
- The `/studietilbud/emner/` URLs are rendered in the browser, so the harvest uses `/for-studenter/Studie-%20og%20emneplaner/emneplan/{CODE}` (#55)

---

### NMBU (Norwegian University of Life Sciences)

- Only the plan in force is published (`plan_years = "current"`; see "Year coverage"); few course codes. Rows without a plan are 404s for discontinued courses, or spring 2025 offerings

---

### Nord (Nord University)

- Year and semester in the URL, with Norwegian characters (`HØST`/`VÅR`); ASCII `HOEST` falls back to a generic page without year-specific content (#126, #129)
- Accordion pages, read with a multi-element selector

---

### NTNU (Norwegian University of Science and Technology)

- Year in the URL, no semester. Pages saying no information is available raise `ntnu_no_info_error`; robots.txt asks for a 10-second crawl delay
- `.anon_ntnu()` cuts from "Kontaktinformasjon" to the end (teachers, exam dates, timetable)

---

### OsloMet (Oslo Metropolitan University)

- The URL always uses `HØST`: spring URLs return 404 and the plan is the same (#1). Pattern: `https://student.oslomet.no/studier/-/studieinfo/emne/{CODE}/{YEAR}/HØST`
- Re-harvested 2026-02-14 after the site moved to server-side rendering (#57, #61). Error pages ("Siden du leter etter finnes ikke") become NA in the anonymizer
- **Practicum courses have no sections** (M1GP\*/M5GP\*, 135 offerings): every section of the course plan only says "Se fagplanen." The page's "Fagplan" block is the programme-wide practicum plan for all study years, with no markup separating the years, so it is not read into the course's sections. Their `course_plan` keeps the full page text (see #242)

---

### Samas (Sámi University of Applied Sciences)

- `noop` strategy, no plans: the website's course codes (SÁM-1005, DUO-1014, ...) do not correspond to DBH codes (V1SAM-1100-1, ...), and the V1/V5 teacher education courses appear only in programme PDFs without per-course descriptions (#69-#72, #85, #89, #90)

---

### Steiner (Rudolf Steiner University College)

- Only the plan in force is published (`plan_years = "current"`; see "Year coverage"). Plans come from five subject PDFs at `steinerhoyskolen.no`, split by course heading (#68, #73); the PDFs are not stored, so the split text is the raw data
- The practicum modules (M-LP1/2/3) have no PDF content
- M-PEL2.1/M-PEL2.2 get the PDF's PEL1.4/PEL1.5 plans (`.steiner_remap_pel_emne()`); to be confirmed against the programme description (#225)

---

### UiA (University of Agder)

- The site has plans from 2020 on; earlier years return 404
- DBH registers most courses in both semesters, but UiA publishes one page, so most 404s are the other semester (see "Semester registration in DBH"; #220)
- URL pattern: `https://www.uia.no/studier/emner/{year}/{semester}/{course_code}.html`

---

### UiB (University of Bergen)

- Year in the URL; accordion pages read with a multi-element selector; robots.txt asks for a 10-second crawl delay
- The page's semester picker is dropped when the HTML is parsed (#219)
- About 280 pages say "Vi opplever problemer med å hente inn eksamensinformasjon": UiB's exam information service fails for these courses, in every year. Fetching the 294 affected pages again on 2026-10-02 fixed 7, so it is not a harvest error. The banner is removed from the sections, and these courses have no assessment text (#219)

---

### UiO (University of Oslo)

- Only the plan in force is published (`plan_years = "current"`; see "Year coverage"). Semester URLs (`/h24/`, `/v25/`) hold logistics (teachers, timetable, exam dates), not the plan (#76)
- Needs faculty/department slugs derived from `Avdelingsnavn` (mapping in `add_course_url_uio()`). Pattern: `https://www.uio.no/studier/emner/{faculty}/{inst}/{CODE}/`
- `.anon_uio()` cuts the generic "Mer om eksamen ved UiO" tail (#224)

---

### UiS (University of Stavanger)

- Current plans come from the course web page, older ones from the PDF archive linked in its semester dropdown (`html_pdf_discovery`, #127); the PDFs are not stored, so their text is the raw data
- Web pages are read from the blocks of `.article__section`, without navigation, facts box and contact footer (#251)

---

### UiT (The Arctic University of Norway)

- **Historical plans** via document ids from the course page's semester picker (see #113)
- The plan is read from `.mainContent` (since #218; the old `.hovedfelt > main > div.col-md-12` matched nothing after a site change, so the 2026-10 harvest first had no text)
- `.pre_uit()` removes the "OBS! Dette emnet tilhører et tidligere semester / år" banner and cuts from "Andre år og semester" / "Kontakt oss" (staff names and e-mails) to the end
- Some pages say "Error rendering component" where the plan should be: the plan failed to render on UiT's site (see #64), and these rows have no text

---

### USN (University of South-Eastern Norway)

- Most rows without a plan are the other semester of a course registered in both (see "Semester registration in DBH"; #221)
- The URL holds a plan version (1-5) that metadata cannot give: `https://www.usn.no/studier/studie-og-emneplaner/#/emne/{CODE}_{VERSION}_{YEAR}_{SEMESTER}`. Invalid version/year combinations silently show another page, so `resolve_urls_usn_batch()` renders each candidate in Chrome and checks the displayed year (README "Institution-Specific Notes")
- Content is rendered in Shadow DOM and read with `read_usn_live_html()`
